---
title: "VAR_XGB"
output:
  pdf_document: default
  html_document: default
  word_document: default
date: '2022-05-27'
---

```{r}
library(quantmod)
library(tidyquant)
library(tidyverse)
library(readr)
library(pastecs)
library(PerformanceAnalytics)
library(lubridate)
library(taskscheduleR)
library(RPostgreSQL)
library(reshape2)
library(TTR)
```


```{r}
con <- DBI::dbConnect(RPostgres::Postgres()
                      , host='localhost'
                      , port='5432'
                      , dbname= 'postgres'
                      , user='postgres'
                      , password="Chui1234!")
```

```{r}
from_date <- "2022-07-01"
```


# industry
```{r}#
library(plyr)
library(vars)
all_industry <- dbGetQuery(con, "SELECT * from all_industry;")
industry_list <- distinct(all_industry, Industry)

for (j in 1: nrow(industry_list)){
  selected_industry <- industry_list[1,]

target_industry <- all_industry %>%
  filter(Industry == selected_industry)
stocks <- target_industry$symbol
stock <- xts()
for (i in 1:length(stocks)){
  stock1 <- getSymbols(stocks[[i]],from = "2022-06-01", to = Sys.Date(), auto.assign = FALSE)
  stock <- merge(stock,stock1[,4])
}
forecast_horizon <- 20
Model <- VAR(stock, p = 1, type = "both")
pred <- predict(Model, n.ahead = forecast_horizon, ci = 0.98, dumvar = NULL)
var_pred <- data.frame(unlist(pred$fcst[1])[1:forecast_horizon])
for (k in 2: nrow(target_industry)){
  var_pred <- cbind(var_pred, unlist(pred$fcst[k])[1:forecast_horizon])
}
colnames(var_pred) <- colnames(stock)
dbWriteTable(con, paste0("var_", selected_industry), var_pred)
rm(var_pred)
}
```

```{r}
#dbWriteTable(con, paste0("var_", selected_industry), var_pred)
#rm(var_pred)
```


## Cointegration 
## Stationary test for multivariate time series
# root() < 1 indicates stationary 
```{r}
roots(Model)
```

## Select optimal lag order
```{r}
VARselect(all_obj_diff, lag.max = 10, type = 'const')
```

## Diagnostic Testing 

# Normality test
```{r}
normality.test(Model)
```

## Serial test
# Leftover pattern in the residual. Close to 2 indicates no significant 
```{r}
serial.test(Model)
```

## Causality test
#For CI = 95%, p value <0.05 indicates variable x cause y 
```{r}
causality(Model, cause = c("X0020.HK.Close", "X3800.HK.Close"))
```




```{r}#
# Stationary Test
#install.packages("aTSA")
library(aTSA)
# ADF test is used to determine the presence of unit root in the series and hence helps in understand if the series is stationary or not
# The null hypothesis is rejected when p <= 0.05 => it's stationary. Otherwise, it is non stationary
for (i in 1:ncol(all_obj)){
  adf.test(all_obj[,i])
}
``` 


```{r}
library(dplyr)
library(xgboost)
train.Dmatrix <- train[,c(-1,-15)] %>% 
  #dplyr::select(CloseDiff, OpenDiff, HighDiff, LowDiff, AdjustedDiff, macdDiff, signalDiff, rsiDiff, DCHighDiff, DCMidDiff,DCLowDiff) %>% 
                 as.matrix() 
                
pred.Dmatrix <- var_pred[,-1] %>% 
    #dplyr::select(CloseDiff, OpenDiff, HighDiff, LowDiff, AdjustedDiff, macdDiff, signalDiff, rsiDiff, DCHighDiff, DCMidDiff,DCLowDiff) %>% 
                as.matrix() 
targets <- train$pred
```

```{r}
#Cross-validation
#install.packages("caret")
library(caret)
xgb_trcontrol <- trainControl(
  method = "cv", 
  number = 10,
  classProbs = TRUE,   
  savePredictions = "final",
#summaryFunction = twoClassSummary,
  allowParallel = TRUE, 
  verboseIter = FALSE, 
  returnData = FALSE
)

#Building parameters set
xgb_grid <- base::expand.grid(
  list(
    nrounds = seq(50,100),
    max_depth = c(6,15,20), 
    colsample_bytree = 1, 
    eta = 0.5,
    gamma = 0,
    min_child_weight = 1,  
    subsample = 1)
)
```

```{r}
#Building stocke model
#install.packages("e1071")
library(e1071)
model.xgb <- caret::train(
  train.Dmatrix,targets,
  trControl = xgb_trcontrol,
  tuneGrid = xgb_grid,
  method = "xgbTree",
  nthread = 10,
  verbosity = 0
)
```

```{r}
model.xgb$bestTune
```

```{r}
#Making stock variables used in forecast object 
fitted <- model.xgb %>%
  stats::predict(train.Dmatrix) %>%
  stats::ts(start=c(2021,9), end =c(2022,5), frequency=365)

ts.xautrygram <- ts(targets, start=c(2021,9), end =c(2022,5), frequency=365)
forecast.xgb <- model.xgb %>% stats::predict(pred.Dmatrix)
forecast.ts <- ts(forecast.xgb,start=c(2022,5),end =c(2022,7), frequency=365)

#Preparing forecast object
forecast.xautrygram <- list(
  model = model.xgb$modelInfo,
  method = model.xgb$method,
  mean = forecast.ts,
  
  x = ts.xautrygram, 
  fitted = fitted,
  residuals = as.numeric(ts.xautrygram) - as.numeric(fitted)
)
class(forecast.xautrygram) <- "forecast"
```

```{r}
#install.packages("Ckmeans.1d.dp")
library(forecast)
#Feature importance
xgb.imp <- xgb.importance(
  feature_names = colnames(train.Dmatrix),
  model = model.xgb$finalModel)

xgb.ggplot.importance(xgb.imp,n_clusters = c(2))+ 
  ggtitle("") +
  theme_bw()+
  theme(legend.position="none")

#xgb.imp$Importance
```

```{r}
# predict values in test set
y.preds = predict(model.xgb, var_pred)
err <- mean(y.preds != test$pred[1:forecast_horizon])
err
```